---
title: "Homework4"
author: "Jacob Brionez"
date: "November 14, 2016"
output: html_document
---

## Introduction
  "This R markdown document is for completion of Homework 4"

##Assignment
  "Write bootstrap code to illustrate the central limit theorem in R markdown and push the result to GitHub." 
  "Use a normal distribution with two different sample sizes and an exponential distribution with two different sample sizes." 
  "Correct code alone is insufficient. "
  "Please also comment on the code and explain the results. "

Sample size 50 normal distribution
```{r}
  x <- rnorm(50, 22, 5)
  xbar <- mean(x)
  xbar
  
  nsims <- 1000 #number of replications
  bootnorm <- numeric(nsims)
  for (i in 1:nsims) {
    temp <- sample(x, 50, replace=TRUE) 
    bootnorm[i] <- mean(temp)
  } 
  #for loop to generate 1000 bootstrap means for this sample of 50 observations
  summary(bootnorm) 
  hist(bootnorm) #to show is normally distribution
  sd(x) #standard deviation of x
  sd(bootnorm) #standard deviation of bootnorm
  sd(x)/sqrt(50) #close to sd(bootnorm) to illustrate CLT
```

Sample size 25 normal distribution
```{r}
  x <- rnorm(25, 22, 5)
  xbar <- mean(x)
  xbar
  
  nsims <- 1000 #number of replications
  bootnorm <- numeric(nsims)
  for (i in 1:nsims) {
    temp <- sample(x, 25, replace=TRUE) 
    bootnorm[i] <- mean(temp)
  } 
  #for loop to generate 1000 bootstrap means for this sample of 50 observations
  summary(bootnorm) 
  hist(bootnorm) #to show is normally distribution
  sd(x) #standard deviation of x
  sd(bootnorm) #standard deviation of bootnorm
  sd(x)/sqrt(25) #close to sd(bootnorm) to illustrate CLT
```

Sample size 50 exponential distribution
```{r}
  x <- rexp(50, 22)
  xbar <- mean(x)
  xbar
  
  nsims <- 1000 #number of replications
  bootnorm <- numeric(nsims)
  for (i in 1:nsims) {
    temp <- sample(x, 50, replace=TRUE) 
    bootnorm[i] <- mean(temp)
  } 
  #for loop to generate 1000 bootstrap means for this sample of 50 observations
  summary(bootnorm) 
  hist(bootnorm) #to show is normally distribution
  sd(x) #standard deviation of x
  sd(bootnorm) #standard deviation of bootnorm
  sd(x)/sqrt(50) #close to sd(bootnorm) to illustrate CLT
```

Sample size 25 exponential distribution
```{r}
  x <- rexp(25, 22)
  xbar <- mean(x)
  xbar
  
  nsims <- 1000 #number of replications
  bootnorm <- numeric(nsims)
  for (i in 1:nsims) {
    temp <- sample(x, 25, replace=TRUE) 
    bootnorm[i] <- mean(temp)
  } 
  #for loop to generate 1000 bootstrap means for this sample of 50 observations
  summary(bootnorm) 
  hist(bootnorm) #to show is normally distribution
  sd(x) #standard deviation of x
  sd(bootnorm) #standard deviation of bootnorm
  sd(x)/sqrt(25) #close to sd(bootnorm) to illustrate CLT
```
